Measuring cross correlation function line-profile variations in radial-velocity measurements via a Skew Normal distribution

### 2018-04-13 manuscript.tex
Add files via upload
updated manuscript

For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).  The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.  However, this would give a noisy estimate so first a normal density shape is fitted to the CCF, and then the estimated mean of the normal density is used as the estimate of the RV.  The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.

The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun. The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}. 
\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
The strength of the asymmetry depends not just on the velocities, it is more complicated than that. It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}. Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a normal distribution can be an appropriate model for the CCF. This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc. The authors are confusing the readers here. They talk about a changing activity signal, but now argue that the precision is only kept if the asymmetry is constant, which it is not. I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Issues with detecting stellar activity}
Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry. All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved. 
\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction. You have a CCF and you measure a width and bisector span. This is a measurement error determined by the S/N, the resolution, and the stability of the spectrograph. You can determine an error in a quantity (RV and BIS). You can also have an uncertainty in the contribution of activity to the RV signal, but that is not a formal error. True errors come from photon statistics, systematic errors, instrumental errors, etc. You can attempt to remove the signal due to activity and that has an associated error, but that error is due to your lack of knowledge of the surface structure causing this RV and the exact value of the contribution to the RV. This is different from a measurement error. Maybe that is what you mean here, but it is not clear from what is written.}
In addition, the normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors. We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Outline of paper}
\todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. In Sec.~\ref{sec:31} we present a simple model to correct for stellar activity. In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators. In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{The Skew Normal distribution} \label{sec:2}
\jessi{I re-wrote this section to hopefully address the referees concerns along with removing elements that are not needed}
\comment{17) I cannot find where R, R+, x and w were defined. It is a common practice when you introduce variables in a paper, these should all be defined.
18) Paragraph 4: "By using the so-called direct parameterization (DP) defined in Eq. 2 problems with parameters estimation arise in the evaluation of the likelihood function in a neighborhood of $\alpha$ = 0, where the presence of a stationary point complicates the achievement of the maximum likelihood or least squares estimates."
A poorly constructed sentence that simply confuses me! The authors are trying to say too many things in one sentence which loses the reader.
19) To be honest, I could not follow all the mathematics. I really would have to read the referenced material, but I had little time. Maybe the details can be put in an appendix?}

The Skew Normal (SN) distribution is a class of probability distributions which includes the normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution.

Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right)
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} normal distribution\footnote{A standard normal distribution is a normal distribution with a mean of 0 and a standard deviation of 1.}
 and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.  We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Figure \ref{fig:SN.plot}.  A usual normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.  If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard normal random variable is less than or equal to 0, which is $0.5$.  The $0.5$ cancels with the $2$ in the denominator and what remains is the usual normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_normal_densities_jjck.pdf} 
   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
Note that the solid black line has an $\alpha = 0$ making it a normal distribution.   
   }
   \label{fig:SN.plot}
\end{figure}

For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).  We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$, and a skewness parameter $\gamma$.  In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the Equation~\eqref{def:snd_gen} with $(\xi, \omega^2, \alpha)$ by
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2}
\end{equation}
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$.

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Figure~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and the variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.  
%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.454\\
6	&	 0.787	&	 0.381	&	 0.891\\
10	&	 0.794	&	 0.370	&	 0.956\\
\hline
   \end{tabular}
   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Figure~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.  Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Equation~\eqref{def:snd_gen} (called the \emph{Direct Parametrization}), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
The SN density shape is used to model the CCF.  In particular, the following function is fit using least-squares estimation,
%
\begin{eqnarray} \label{eq:3}
f_{CCF}(y_i) = \mathrm{C} - \mathrm{A} \times SN(y_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
\end{eqnarray}
%
where C is a constant fitting the continuum of the CCF \jessi{The C is unclear to me - can more intuition be added here?  Are C and A considered known?}, A is an amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF. Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.

Since each point of the CCF has a measurement error, this information is included in the specification of the SN distribution by introducing the following heteroskedastic function for the variance,
%
\begin{equation}
\text{var}(Y_{i})=\sigma^{2}+\sigma_{i}^{2}, \quad i = 1, \dots, n,
\label{eq:vaf}
\end{equation}
%
where $\sigma_{i}$ represents the measurement error for each point of the CCF. By using Eq. \ref{eq:vaf} we can interpret the parameter $\sigma^{2}$ \jessi{this is going to be confusing given the CP parametrization of the SN - one needs to be changes} as a measure of the pure variability present in the evaluation of the CCF. 
However, although useful for estimating correct error bars in the case where the different $\sigma_{i}$ do not include all systematics, this heteroskedastic function only considers Gaussian distributed residuals. \jessi{the previous statement is unclear}
%

The CCF is the result of a cross correlation so the residuals of a Normal or a SN fit are expected to show correlated noise.
To investigate this issue, we considered example CCFs from the star Tau Ceti.  The CCFs were modeled using a normal or a SN shape, and assuming independent normally-distributed noise around the modeled shape. 
%
We then subtracted the median of the residuals (the original data minus the fit function) obtained for all CCFs before performing a second round of fitting. The result of this procedure is illustrated in Figure~\ref{fig:Residual.comparison}. The lower left panel displays the residuals of a simple fit of a normal or a SN distribution, which appear to be strongly correlated. 
%
After removing the median of the residuals, in the lower right panel, the final residuals of the SN procedure have almost no apparent correlation, while the final residuals of the Normal procedure still present a small systematic component. This seems to be due to the asymmetric nature of the CCF (see Section~\ref{intro}), which is not captured in a symmetric distribution like the normal distribution.  This exercise highlights that the SN density shape better captures the shape of a CCF compared to a normal density shape.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 6in]{[1]Plot_Fitting_and_Residuals_2run.pdf} 
   \caption{Comparison between the Normal and the SN procedures for modeling a collection of CCFs for the star Tau Ceti.  Two stages of modeling are carried out with the first stage results displayed in the left column and the second stage in the right column.
   The first run corresponds to fitting a normal or a SN shape to the raw CCF. The second run corresponds to fitting the same shape to the CCF after removing the median of all the residuals obtained in the first run. The SN residuals of the second run present minimal correlations, whereas the normal residuals present still a clear systematic component.}
   \label{fig:Residual.comparison}
\end{figure*}
%When using the least squares estimate for fitting the CCF with the SN distribution, we have to take into account the stationary problem in $\gamma=0$ due to the presence of the function $sign(\gamma)$ in Equation (\ref{eq:2}). Depending on the initial values of the numerical minimization for the least squares estimate of $\gamma$, the presence of this stationary point when evaluating $\gamma$ can lead to an incorrect estimation of the asymmetry parameter of the SN. In order to resolve this problem, we implemented two functions for retrieving the best least squares solution. In the first function we allowed for only positive solutions of $\gamma_1$ (with an upper limit of $0.995$), while in the second function only negative solutions are allowed (with a lower limit of $\gamma= -0.995$). The chosen solution is the estimate which has smallest residuals.

In the following of the paper, we define the RV as the mean of the normal or the mean of the SN (defined as SN RV). For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$. The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}. In the Normal case, there is not an asymmetric parameter so we use BIS SPAN. This will be compared to the asymmetric parameter $\gamma_1$ of the SN. \jessi{Why use FWHM at all?  Why not just use the standard deviation since the FWHM just includes a multiplicative factor that is the same for all of them.}

\section{Effect of stellar activity on radial velocities and correction} \label{sec:31}

An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines. To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, \jessi{citations are needed here} which provide information on the average width and asymmetry of the CCF. A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity.

To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.

To correct for stellar activity signals, it is common to consider a linear combination of the RVs with the BIS SPAN and the FWHM (or $\gamma$ and SN FWHM in the SN case):
\comment{Is this really common? I am not aware of it having wide use in the community. If so, references would support this. The authors have to distinguish what their research group and collaborators do from what the rest of the community does.}
%
\begin{equation}
RV= \beta_{0} + \beta_{1}  \gamma + \beta_{2} FWHM + \epsilon,
\label{eq:RV:correction}
\end{equation}
%
where $\beta_{0}$ is the intercept and $\epsilon$ is the vector of the errors with mean equal to $0$ and covariance matrix equal to $\sigma^{2}I$ ($I$ is the identity matrix). 
\comment{Is this expression just for the RV from activity alone, or the measured RV from the star (contribution of all phenomena)? If it is just activity, you should put a subscript otherwise the readers will be confused. In the text you refer to the variable ?1, but Eq. 9 has no subscript in ?. You give one equation for Normal and SN, but in the text you state these variables have to be replaced by such and such when using SN, etc. It will be less confusing if you simply have two equations, one for Normal and one for SN and with their respective variables.}
When the Normal fit is used, the parameter $\gamma_1$ is replaced by the BIS SPAN and SN FWHM by FWHM. In order to show the goodness of this correction, a statistical test on the parameters $\beta_{0}$, $\beta_{1}$ and $\beta_{2}$ is presented, where the null hypothesis is $H_{0}: \beta_{i}=0$, for $i=0,1,2$. \jessi{the estimated values and p-values of the $\beta$'s does \underline{not} show goodness of fit.}
The level for not rejecting the null hypothesis is fixed equal to $0.05$. Pearson correlation coefficient $R^{2}$ is considered for explaining how well this linear combination explains the variability of the RVs of the star due to stellar activity. \jessi{$R^2$ is the coefficient of determination, and this should be explained better because it is not commonly used in astronomy as an assessment of the amount of variability explained by the model.}

@@

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Real data applications} \label{sec:4}
\jessi{I suggest we include one real-date application (whichever is used in \S\ref{sec:soap_real} (Alpha Centauri B?) and then add the other examples to an appendix}

In this Section we present the analyses of five stars comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} versus the Normal approach.

A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by the mean of the Normal distribution used to fit the CCF along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}.

@@

Alpha Centauri B $1816$ CCFs in 2010 are considered. Several measurement in 2010 are contaminated by light from Alpha Centauri A. To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}.

We begin by evaluating the correlation between $\gamma$ and the BIS SPAN. In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.933$ and a strong Pearson correlation coefficient of $0.958$. \jessi{It would be good to explain why you care about this.}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B.}
   \label{fig:alphacent:corr.gamma}
\end{figure}

>>>>

For stabilized spectrographs, the RV is derived by first correlating a stellar spectrum at a particular time with a synthetic \citep[][]{Baranne-1996,Pepe-2002a} or an observed stellar template \citep[][]{Anglada-Escude-2012}, which gives an average line profile, generally called Cross Correlation Function (CCF).  The CCF is a function of RV, and the RV corresponding to the minimum of the CCF is the estimated RV for that spectrum.  However, this would give a noisy estimate so first a Normal density shape is fitted to the CCF, and then the estimated mean of the Normal density is used as the estimate of the RV.  The full width at half maximum (FWHM) of the Normal fit is also used as an indicator of spectral line asymmetry.
The CCF technique allows for an averaging of thousands of spectral lines and can therefore reach a very high signal-to-noise ratio (SNR), which is essential for a good RV precision.

The convection in external layers of solar type stars is responsible for the granulation pattern than can be seen at high spatial resolution on the surface of the Sun. The differences in flux and velocity between upflows and downflows change the Normal profile of spectral lines that become asymmetric with a "C"-shaped profile \citep[][]{Dravins-1981}. 
\comment{Regarding the C-shape of the bisector. The classic C-shape is only for late-type stars. In fact for hotter stars (F-type) it reverses.
The strength of the asymmetry depends not just on the velocities, it is more complicated than that. It also depends on the flux ratio between hot cells and cool lanes, as well as the ratio of surface areas between the two.}
The strength of the asymmetry depends on the velocity of the convection, approximatively 300\ms for the Sun, but also on the formation depth of spectral lines \citep{Gray-2009}. Since the CCF is an average of all the spectral lines, some strongly asymmetric and some not, its asymmetry is rather small, which is why a Normal distribution can be an appropriate model for the CCF. This small asymmetry modifies however slightly the estimated RVs of the star, reducing the accuracy of the measurement, but if this asymmetry does not vary with time, the precision is kept.
\comment{But the activity causes the asymmetry to change due to rotation, spot evolution, etc. The authors are confusing the readers here. They talk about a changing activity signal, but now argue that the precision is only kept if the asymmetry is constant, which it is not. I think what they want to say is that you measure a precise stellar radial velocity, but the activity makes its own contribution which reduces the accuracy of the RV determination for the barycentric motion due to a planet.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Issues with detecting stellar activity}
Unfortunately, when analyzing slow rotators stars such as the Sun, due to the limited spectral resolution of the spectrographs and the limited precision in RV, it becomes difficult to measure the line asymmetry, resulting in complications for detecting very small-mass planets with the RV technique.
In the procedure described above, the measurement of the RV and the FWHM is done separately from the measurement of the line asymmetry. All those parameters are correlated when stellar activity is dominant, and performing a step-by-step approach makes it difficult to correctly derive the errors on the different parameters retrieved. 
\comment{I simply do not understand this statement, possibly because it does not follow a standard English construction. You have a CCF and you measure a width and bisector span. This is a measurement error determined by the S/N, the resolution, and the stability of the spectrograph. You can determine an error in a quantity (RV and BIS). You can also have an uncertainty in the contribution of activity to the RV signal, but that is not a formal error. True errors come from photon statistics, systematic errors, instrumental errors, etc. You can attempt to remove the signal due to activity and that has an associated error, but that error is due to your lack of knowledge of the surface structure causing this RV and the exact value of the contribution to the RV. This is different from a measurement error. Maybe that is what you mean here, but it is not clear from what is written.}
In addition, the Normal distribution cannot take into account the natural asymmetry of the CCF, leaving correlated noise in the residuals, which also complicates the determination of errors. We propose to overcome these problems by fitting a SN (SN) distribution to the CCF, which naturally includes a skewness parameter \citep[][]{Azzalini1985}.

\umberto{We considered CCFs having SNR larger than 10.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Outline of paper}
\todo{This paragraph will need to be updated once the rest is finished.} The paper is organized as follow. In Sec.~\ref{sec:2} we introduce the SN distribution and describe its applicability for modeling the CCF,  show that the SN density is a better representation of observed CCF than a Normal distribution, and study how the SN parameters relate to the RV, FWHM and BIS SPAN of the CCF. In Sec.~\ref{sec:31} we present a simple model to correct for stellar activity. In Sec.~\ref{sec:4}, we compare on real observations the sensitivity of the SN parameters to stellar activity with respect to other existing indicators. In Sec.~\ref{sec:5} we derive error bars for the different CCF parameters, and finally we discuss our results and conclude in Sec.~\ref{sec:discu} and Sec.~\ref{sec:conclu}.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{The Skew Normal distribution} \label{sec:2}

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right)
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}
 and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.  We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~ \ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Equation~\eqref{def:snd_gen}.  If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard Normal random variable is less than or equal to 0, which is $0.5$.  The $0.5$ cancels with the $2$ in the denominator and what remains is the usual Normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$, and different values of the skewness parameter $\alpha$ indicated by different colors and line types.
Note that the solid black line has an $\alpha = 0$ making it a Normal distribution.   
   }
   \label{fig:SN.plot}
\end{figure}
%
For reasons related to the interpretation of the parameters in Equation~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).  We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$, and a skewness parameter $\gamma$.  In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the Equation~\eqref{def:snd_gen} with $(\xi, \omega^2, \alpha)$ by
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2}
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$.

By using Eq. \ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Fig.~~\ref{fig:SN.plot}, the corresponding values of $\mu$, $\sigma^2$, $\gamma$ are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter), and $\gamma$ becomes an index for evaluating the asymmetry of the SN.

Beyond the mean of the SN, it is convenient to introduce a second location parameter that will be largely used in the analyses: the median. The median of the SN is defined as that value $m$ such that 
%
\begin{equation} \label{eq:snmed}
\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2},
\end{equation}
%
where $SN(y;\xi, \omega, \alpha)$ follows Equation \ref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}

%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.454\\
6	&	 0.787	&	 0.381	&	 0.891\\
10	&	 0.794	&	 0.370	&	 0.956\\
\hline
   \end{tabular}
   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Fig.~~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Equation~\eqref{eq:snd_cp}.  Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Equation~\eqref{def:snd_gen} (called \emph{Direct Parametrization} or DP), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
The SN density shape is used to model the CCF.  In particular, the following function is fit using least-squares estimation,
%
\begin{eqnarray} \label{eq:3}
f_{CCF}(y_i) = \mathrm{C} - \mathrm{A} \times SN(y_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
\end{eqnarray}
%
where C is a constant fitting the continuum of the CCF \jessi{The C is unclear to me - can more intuition be added here?  Are C and A considered known?}, A is an unknown amplitude parameter, and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF. Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.

Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution can better catch this aspect, together with other changes in asymmetry, respect the Normal fit. To check this assumption, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars. The first star is Alpha Centauri b, whose CCFs have high signal to noise ratio (SNR). The second star is Corot-7, whose CCFs have low SNR. Fig.~ \ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{[1]HD128621Residuals.pdf} 
\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCFs of the star Alpha Centauri b (left) and Corot-7 (right). The results are comparable looking at the residuals corresponding to the tails of the CCF but the SN fit leads to slightly better results in the center of the CCF for both the stars. As the signal to noise decreases, as happens when analyzing the star Corot-7, the SN distribution leads to better residuals respect using the Normal.}
    \label{fig:Residual.comparison}
\end{figure*}
%

\subsection{Effect of stellar activity on the CCF} \label{sec:31}

An orbiting exoplanet will produce an RV variation induced by a pure Doppler shift of \emph{all} the spectral lines of each stellar spectrum. 
Stellar activity, however, does not produce a blueshift or redshift of the spectra, but can create a spurious RV signal by modifying the shape of spectral lines. To track changes in line shape, the FWHM, the BIS SPAN or the indicators introduced by \citet{Figueira-2013} are often used, which provide information on the average width and asymmetry of the CCF \citep{Hatzes1996, fiorenzano2005line, Queloz-2001}. A strong correlation between the estimated RVs and one or more of these parameters is a sign that the estimated RVs may be contaminated by stellar activity. To test the strength of the correlation between RVs and the different activity indicators, we calculated the Pearson correlation coefficient, $R$.
A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ (i.e., no correlation) is provided, along with a $95\,\%$ confidence interval for $R$.

In the following of the paper, we define RV as the mean of the Normal. Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV (i.e. looking at Equation \eqref{eq:snmed}, $m$ = SN median RV). We will discuss advantages and limits for both these choices in the examples. For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$. The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}. Being a Normal distribution symmetric, there is not such a parameter that evaluates the asymmetry of the distribution, so the BIS SPAN is used. This will be compared to the asymmetric parameter $\gamma$ of the SN, called SN GAMMA.

@@

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Real data applications} \label{sec:4}

In this Section we present the analyses conducted on Alpha Centauri b, comparing the result of fitting a CCF using the SN distribution defined in Section \ref{sec:3} versus the Normal approach. Other 4 stars have been analyzed with the proposed methods and details can be found in the Appendix \ref{appendix}. A comparison with the results obtained by the classic approach is done, where the RVs of the star are estimated by retrieving the mean of the Normal distribution used to fit the CCF, along with the BIS SPAN or the other asymmetric parameters defined in \citet{Figueira-2013}. The latter parameters are calculated separately from the Normal fit that leads to the RV of the star.

@@

A total of $1808$ CCFs measured in $2010$ have been analysed from the star Alpha Centauri B. Several measurement in 2010 are contaminated by light from Alpha Centauri A. To remove contaminated spectra and thus CCFs, we performed the same selection as presented in \citet{Dumusque-2012}. Moreover, as noted in \citet{Dumusque-2012} and \citet{Thompson-2017}, this dataset presents a strong stellar activity signal.

We begin by evaluating the correlation between $\gamma$ and the BIS SPAN. In Fig.~\ref{fig:alphacent:corr.gamma}, we see that the relationship between $\gamma$ and the BIS SPAN is linear, with a slope equal to $0.99$ and a strong Pearson correlation coefficient of $0.96$. This comparison is useful because $\gamma$ is an adimensional parameter taking information about the asymmetry of the SN while the BIS SPAN, beyond this, has got unit of measure of \kms. In other words, by using Fig.~\ref{fig:alphacent:corr.gamma}, it is possible to provide to $\gamma$ a physical meaning.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{HD12862_[2]gamma_vs_bisspan.pdf} 
   \caption{Correlation between $\gamma$ and the BIS SPAN for Alpha Centauri B. Because $\gamma$ is adimensional, retrieving the slope between $\gamma$ and the BIS SPAN, which is expressed in \kms, allows us to provide physical meaning to $\gamma$.}
   \label{fig:alphacent:corr.gamma}
\end{figure}
%
